---
output:
  pdf_document: default
  html_document: default
---

---
title:  Decision Analysis Template
author: "Cory Whitney, Eike Luedeling et al."
output: 
  learnr::tutorial:
runtime: shiny_prerendered
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
install.packages("knitr")
library(knitr)
install.packages("learnr")
library(rmarkdown)
library(learnr)
library(tidyverse)
```

The following videos tell you something about a method which is frequently used
in our group to get reliable values for the input tables from our stakeholders. 
Please watch the videos and answer the questions that follow. 

### Explaining calibration training Part 1

<!-- THis will also work, but not in html ![](https://youtu.be/pPIs7MwgMe0) -->

![](https://youtu.be/pPIs7MwgMe0)

<!-- Note that the youtube link needs to begin with https://www.youtube.com/embed/ -->

<iframe width="560" height="315" src="https://www.youtube.com/embed/DYAv-LBZaIU" frameborder="0" allowfullscreen></iframe>

```{r question-explaining-calibration-training-part-01-01, echo=FALSE}
question("What is the intention of decision analysts in measuring things?",
  answer("They want to get paid for."),
  answer("They want to get precise information."),
  answer("They follow what the research project tells them to do."),
 answer("They want to reduce their uncertainty.", correct = TRUE),
 answer("They are inspired by Douglas Hubbart and measure anything."), 
  incorrect = "Watch [the video](https://youtu.be/DYAv-LBZaIU) and try again.",
allow_retry = TRUE
)
```

<!-- Note that the youtube link here is standard https://youtu.be/pPIs7MwgMe0 -->
<!-- We can add anything we want here in the incorrect response (or nothing) -->

```{r question-define-decision-part-01-02, echo=FALSE}
question("What is missing?",
answer("Decision-maker", correct = TRUE),
answer("Concrete options", correct = TRUE),
answer("Relevant issue in agricultural development"),
answer("Clear context", correct = TRUE),
  incorrect = "Watch [the video](https://youtu.be/pPIs7MwgMe0) and try again.",
allow_retry = TRUE
)
```

### Explainig Calibration Training Part 2

<!-- ![](https://youtu.be/4vlwELJwHYg) -->

<iframe width="560" height="315" src="https://www.youtube.com/embed/4vlwELJwHYg" frameborder="0" allowfullscreen></iframe>

Think about the following questions and jot down your thoughts.

- **Does decision analysis make sense without involving a decision-maker?**
- **What can this achieve, and what shouldn't we expect from it?**

### Defining Decisions Part 3

<!-- ![](https://youtu.be/5ZTd73gcL-0) -->

<iframe width="560" height="315" src="https://www.youtube.com/embed/5ZTd73gcL-0" frameborder="0" allowfullscreen></iframe>

```{r question-define-decision-part-03-01, echo=FALSE}
question("Which aspects of research should you pay attention to, if you want to maximize the *credibility* of your research?",
answer("Relationship with stakeholders"),
answer("Robust statistics", correct = TRUE),
answer("Inclusive, participatory research"),
answer("Clear experimental design", correct = TRUE),
answer("Alignment with policies and plans"),
answer("Choices actually considered by local actors"),
  incorrect = "Watch [the video](https://youtu.be/pPIs7MwgMe0) and try again.",
allow_retry = TRUE
)
```

```{r question-define-decision-part-03-02, echo=FALSE}
question("Which aspects of research should you pay attention to, if you want to maximize the *salience* of your research?",
answer("Relationship with stakeholders"),
answer("Robust statistics"),
answer("Inclusive, participatory research", correct = TRUE),
answer("Clear experimental design"),
answer("Alignment with policies and plans", correct = TRUE),
answer("Choices actually considered by local actors", correct = TRUE),
  incorrect = "Watch [the video](https://youtu.be/pPIs7MwgMe0) and try again.",
allow_retry = TRUE
)
```

### Group discussion- food for thought
1 What do you think about the idea of taking estimates as values for the impact models?

1 What do you think about the method of calibration training as presented? Do you have suggestions how to change or improve it?

1 Can you think of further cognitive biases and how to deal with them?
### Group discussion reading: 

<!-- We can add citations (they need to be included in the overall .bib file, best way to do that is to make sure it is in the DA group Zotero and export that as .bib ) -->

This week you will all read Kahneman and Egan (2011) (Chapter 1) on cognitive biases. One group will lead a discussion on the reading.


### Bonus Material
Watch the video and do the awareness test!

<!-- ![](https://youtu.be/UfA3ivLK_tE) -->

<iframe width="560" height="315" src="<iframe width="489" height="391" src="https://www.youtube.com/embed/UfA3ivLK_tE" frameborder="0" allowfullscreen></iframe>
